FastSRM: A fast, memory efficient and identifiable implementation of the shared response model

### 2022-01-04 paper/main.tex
typos

In this work, we implement an identifiable version of SRM and show on real data
that it improves the stability of the recovered shared response.
%
We then introduce FastSRM, that relies on a dimension reduction step that we
prove to yield the same solution as the original algorithm.
% be optimal in the sense that working with reduced data does not induce any change in the
% algorithm trajectory.
%
We show experimentally using synthetic and real fMRI data
that FastSRM is considerably faster and more memory efficient
than current implementations.

The experiments performed in the paper are \emph{fully} reproducible: our
code available at \url{https://github.com/hugorichard/FastSRM} allows to download the
data, run the experiments and plot the figures.
%

>>>>

In this work, we implement an identifiable version of SRM and show on real data
that it improves the stability of the recovered shared response.
%
We then introduce FastSRM, which relies on a dimension reduction step that we
prove to yield the same solution as the original algorithm.
% be optimal in the sense that working with reduced data does not induce any change in the
% algorithm trajectory.
%
We show experimentally using synthetic and real fMRI data
that FastSRM is considerably faster and more memory efficient
than current implementations.

The experiments performed in this article are \emph{fully} reproducible: our
code available at \url{https://github.com/hugorichard/FastSRM} allows you to download the
data, run the experiments and plot the figures.
%
